Fail Faster

### 2025-03-23 paper/paper.tex
further fixes on rng section

For example, significantly faster algorithms than SplitMix or JSF exist,
such as the Lehmer algorithm\cn, WyHash \cn, and the xoroshiro family.
These all run between 1.2-1.6x faster per byte than SplitMix in microbenchmarks \cn.
Moreover, plenty of other optimizations on top of algorithm choice exist,
including pipelined or even ahead-of-time sampling.
% https://github.com/lemire/testingRNG/tree/master
% https://github.com/wangyi-fudan/wyhash?tab=readme-ov-file

>>>>

For example, significantly faster algorithms than SplitMix or JSF exist,
such as the Lehmer algorithm~\cite{lehmerrng}, WyRand~\cite{wyrand}, and the xorshiro family of algorithms~\cite{xorshiro}.
These all run between 1.2-1.6x faster per byte than SplitMix in microbenchmarks~\cite{lemiremicrobenchmarks}.
Plenty of other known optimizations on top of algorithm choice could also be implemented,
including pipelined or even ahead-of-time sampling.
% https://github.com/lemire/testingRNG/tree/master
% https://github.com/wangyi-fudan/wyhash?tab=readme-ov-file
